\mytitle

### 2021-12-16 paper.tex
update numbers

In \tabref{tab:runtime} the runtime of different C implementations is
compared on two different CPU architectures.  On each architecture the
implentations are compiled with \texttt{g++} with optimization
\texttt{-O2}.  The shown runtime denotes the total wall clock time for
the calculation of $\Li(x)$ for $10^6$ uniformly distributed random
values $x\in[0,1/2]$.
%
\begin{table}[tb]
  \centering
  \caption{Runtime in seconds for the calculation of $\Li(x)$ for
    different implementations on different CPU architectures with
    different compilers.}
  \begin{tabular}{lcc}
    \toprule
    \multirow{2}{*}{Implementation} & i7-5600U & ?? \\
    & \texttt{g++} 10.2.1 & \texttt{g++} 9.3.0 \\
    \midrule
    this paper                        & $0.0058$ & $??$ \\
    Morris (DILOG 0011) \cite{morris} & $0.0085$ & $??$ \\
    Cephes \cite{cephes}              & $0.0119$ & $??$ \\
    Algorithm 327 \cite{koelbigDilog} & $0.0172$ & $??$ \\
    Chebyshev \cite{luke}             & $0.0515$ & $??$ \\
    Algorithm 490 \cite{ginsberg}     & $0.0576$ & $??$ \\
    GSL \cite{gsl}                    & $0.0898$ & $??$ \\
    \bottomrule
  \end{tabular}
  \label{tab:runtime}
\end{table}
%
We find that the implementation presented in this paper and the
approach presented in \cite{morris} are fastest among the ones shown
in the table.  The next-to fastest implementation is provided by
Cephes, which is only $\sim 20\%$ slower.  The short runtime of Cephes
stems from the fact that Cephes also uses a rational function
approximation, where the numerator and the denominator can be
evaluated in parallel.  However, Cephes evaluates the polynomials in
the numerator and denominator using Horner's scheme, which is purely
sequential.  Furthermore, for $x>1$ Cephes calculates $\ln(x)$ twice,
which leads to a further slowdown.

>>>>

In \tabref{tab:runtime} the runtime of different C implementations is
compared on two different CPU architectures.  On each architecture the
implentations are compiled with \texttt{g++} with optimization
\texttt{-O2}.  The shown runtime denotes the total wall clock time for
the calculation of $\Li(x)$ for $10^6$ uniformly distributed random
values $x\in[0,1/2]$.  The choice of this interval ensures that the
measurement is only sensitive to the formulation of the approximant,
but not to the transformation onto the interval $[0,1/2]$.
%
\begin{table}[tb]
  \centering
  \caption{Runtime in seconds for the calculation of $\Li(x)$ for
    different implementations on different CPU architectures with
    different compilers.}
  \begin{tabular}{lcc}
    \toprule
    \multirow{2}{*}{Implementation} & i7-4700MQ & i7-5600U \\
    & \texttt{g++} 9.3.0 & \texttt{g++} 10.2.1 \\
    \midrule
    this paper                        & $0.0076$ & $0.0058$ \\
    Morris (DILOG 0011) \cite{morris} & $0.0115$ & $0.0085$ \\
    Cephes \cite{cephes}              & $0.0136$ & $0.0119$ \\
    Algorithm 327 \cite{koelbigDilog} & $0.0229$ & $0.0172$ \\
    Chebyshev \cite{luke}             & $0.0718$ & $0.0515$ \\
    Algorithm 490 \cite{ginsberg}     & $0.1057$ & $0.0576$ \\
    GSL \cite{gsl}                    & $0.2091$ & $0.0898$ \\
    \bottomrule
  \end{tabular}
  \label{tab:runtime}
\end{table}
%
We find that the implementation presented in this paper and the
approach presented in \cite{morris} are fastest among the ones shown
in the table.  The next-to fastest implementation is provided by
Cephes, which is only $\sim 20\%$ slower.  The short runtime of Cephes
stems from the fact that Cephes also uses a rational function
approximation, where the numerator and the denominator can be
evaluated in parallel.  However, Cephes evaluates the polynomials in
the numerator and denominator using Horner's scheme, which is purely
sequential.  Furthermore, for $x>1$ Cephes calculates $\ln(x)$ twice,
which leads to a further slowdown.
